### 2018-03-12 Paper/jaccardbaetica.tex
update results and dis
change in conclusion
add new lines conclusion

@@

The correlation coefficients range from a minimum to a maximum. The dendrogram shown in Fig. 2 was obtained with Morisita-Horn index. This dendrogram suggests that amphora workshops used different stamps for their prodution system. Accordingly only few closer workshops show a similarity on the stamps while most of them seem to display different stamps roles.

@@

No strong relation between stamps and spatial distance have been detected in amphora workshops.  
The analysis suggests that there is not connection between stamps and the same amphora workshops so similar stamps between closer amphora workshops were not found, excluding certain exception. Consequently the majority of stamps are located in different amphora workshops.

The hypothesis about groups of amphora workshops sharing the same stamps seems not match with the results of analysis. Rather it could be interpreted due to several reason. On the one hand, the use of this amphoric stamps were exclusively running by the owner or family to distinguish the amphora workshop (CITAR). (EXPLICAR)

On the other, it could be somehow a batch systematic organization to prepare and distribute the commodity, considering that Dressel 20 was not marked in several cases (CITAR).
(EXPLICAR)

%Neither it seems a group of amphora workshops sharing the same stamps.

>>>>

CAMBIAR

@@

The correlation coefficients range from a minimum to a maximum. The dendrogram shown in Fig. 2 \ref{dendro} was obtained with Morisita-Horn index. This dendrogram suggests that amphora workshops used different stamps for their prodution system. Accordingly only few closer workshops show a similarity on the stamps while most of them seem to display different stamps roles.

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/dendro}
\caption{Dendrogram obtained by Morisita-Horn algorithm of different amphora workshops in Baetica area}
\label{dendro}
\end{figure}

@@

No strong relation between stamps and spatial distance have been detected in amphora workshops.  
Indeed, the analysis suggests that there is not connection between stamps and the same amphora workshops, excluding certain exceptions. Consequently the majority of stamps are located in different amphora workshops and only few similar stamps between closer amphora workshops were found.

The hypothesis about groups of amphora workshops sharing the same stamps seems not match with the results of analysis even though there are shareable stamps in closer workshops. Probably same stamps detected in closer amphora workshop could have being wrongly catalogued twice in different way in spite of belonging to the same place or being closer between each other.

%los que aparecen cerca son porque están cerca o puede haber confusión entre talleres

By contrast, we have located different stamps in a same amphora workshop. Neither it seems that stamps were used to specify the quality or value of the product \citep{callender}. Rather our results could be interpreted due to several reason according to previous hypotheses. On the one hand, the use of these amphoric stamps could be exclusively running by the owner or family to distinguish the amphora workshop (CITAR).

(aumentar)
Considering that Dressel 20 type was not marked in several cases (CITAR) it can be interpreted somehow a batch systematic organization to prepare and distribute the commodity (CITAR)

it could be somehow a batch systematic organization to prepare and distribute the commodity, considering that Dressel 20 was not marked in several cases. This method was used of counting BLA BAL
